Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-13 prop_iop.tex
prop_iop.tex \DeclareUnicodeCharacter{0229}{\c{e}} Added to eliminate biblatex error...
prop_iop.tex Elimating pdfLaTeX warnings...

\documentclass[12pt]{iopart}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage{cmap}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}

@@

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }
\newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
\newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}

@@

This section extend the idea of restricting the event space, but instead
of commuting sub-event space, we will try to find some subset~$\events'\subseteq\events$
such that $\bar{\mu}|_{\events'}$ has an non-empty core. This could
help us understand the core because of the following identity
\begin{equation}
\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\label{eq:core-intersection}
\end{equation}
if we know more about the right-hand side of the equation, we can
have more idea about the left-hand side. This idea can be applied
to example~\ref{ex:three-dimensional-three-value}, and the following
are three of all possibilities:
\begin{itemize}
\item When $\events_{1}=\events\backslash\left\{ \proj{\ps'}\right\} $,
because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have
$\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} $.
\item When $\events_{2}=\events\backslash\left\{ \proj{\ps}\right\} $,
because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, we
have $\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} $.
\item When $\events_{3}=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$,
we have $\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$
as well as $\mu_{\ket{2}}^{\mathrm{B}}$ and $\mu_{\ket{1}}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$.
\end{itemize}
Each of these possibilities is compatible with some but not all of
the observations. In another word, 
\begin{equation}
\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} \cap\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} =\emptyset\textrm{ .}
\end{equation}
The first two possibilities are particular interesting since each
two 1-dimensional projectors~$\proj{\psi_{0}}$ and $\proj{\psi_{1}}$
mapped to $\imposs$ suggests there is a subset~$\events'\subseteq\events$
such that $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{\mathrm{B}}\right\} $
in the Hilbert space of dimension 3, where the cross product of complex
vectors is defined in definition~\ref{def:cross-product}.

@@

In order to simplify the discussion, we call a function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$
satisfying conditions in theorem~\ref{thm:interval-valued-frame-function}
a real interval-valued frame function. Obviously, any results in appendix~\ref{sec:Interval-valued-Frame-Functions}
still hold if we replace every ``complex'' by ``real,'' in particular,
replace every $\mathbb{C}S^{2}$ by $S^{2}$. Furthermore, since restricting
the domain of a complex interval-valued frame function to $S^{2}$
gives a real interval-valued frame function, if we prove there is
no real interval-valued frame function satisfying a condition, then
there must be no complex interval-valued frame function satisfying
the corresponding condition. From now on, when we write an interval-valued
frame function~$\bar{f}$ without other specification, we would always
means a real interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$.

@@

\begin{proof}When $\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$,
$\bar{\mu}$ and $\bar{\mu}^{\Omega}$ are essentially quantum and
classical real-valued probability measures, respectively. Hence, it
is sufficient to prove the interval-valued case.
\begin{itemize}
\item $\bar{\mu}^{\Omega}(\emptyset)=\bar{\mu}\left(\sum_{\ket{j}\in\emptyset}\proj{j}\right)=\bar{\mu}\left(\mathbb{0}\right)=[0,0]$. 
\item $\bar{\mu}^{\Omega}(\Omega)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)=[1,1]$. 
\item For any event $E\in2^{\Omega}$,
\begin{equation}
\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .}
\end{equation}
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$
of pairwise disjoint events, we have
\begin{equation}
\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}^{\Omega}\left(E_{i}\right)\textrm{ .}
\end{equation}
\end{itemize}
\end{proof}

@@

For case \ref{enu:sub-event-space-real-classical2quantum}, if we
pick $\rho=\sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\proj{j}$,
then $\rho$ is a density matrix because~\cite{544199}
\begin{eqnarray}
\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\Tr\left(\proj{j}\right)=1\textrm{ .}
\end{eqnarray}
Also, 
\begin{eqnarray*}
 &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)=\sum_{j=1}^{N}\mu'\left(\left\{ j\right\} \right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)=\mu'\left(\left\{ j\right\} \right)=\mu'\left(\tau\left(\proj{i}\right)\right)\textrm{ for all }i\textrm{ ,}\\
 &  & \mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)\overset{\textrm{IH}}{=}\mu'\left(\tau\left(P_{1}\right)\right)+\mu'\left(\tau\left(P_{2}\right)\right)=\mu'\left(\tau\left(P_{1}\right)\cup\tau\left(P_{2}\right)\right)=\mu'\left(\tau\left(P_{1}+P_{2}\right)\right)\textrm{ for commuting }P_{0},P_{1}\in\events\textrm{ with }P_{0}P_{1}=\mathbb{0}\textrm{ .}
\end{eqnarray*}
Therefore, we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\widehat{\events}$ by induction.\end{proof}

@@

\begin{proof}Given two events~$E_{0},E_{1}\subseteq\Omega$, we
want to verify 
\begin{equation}
\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}\label{eq:classical-convex}
\end{equation}
When $E_{0}\cap E_{1}=\emptyset$, equation~(\ref{eq:classical-convex})
is a special case of equation~(\ref{eq:classical-include}). When
$E_{0}\cup E_{1}=\Omega$, we have $E_{0}^{c}\cap E_{1}^{c}=\emptyset$,
where $E_{0}^{c}=\Omega\backslash E_{0}$ and $E_{1}^{c}=\Omega\backslash E_{1}$.
Thus, 
\begin{equation}\eqalign{ 
& \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\ 
\Rightarrow & \left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\left[1,1\right]-\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\ 
\Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\ 
\Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .} 
}\end{equation}
When the number of elements in $\Omega\le3$, either $E_{0}\cap E_{1}=\emptyset$
or $E_{0}\cup E_{1}=\Omega$ must happen so that $\bar{\mu}^{\Omega}$
is convex. \end{proof}

@@

\begin{proof}Since $\left(\mathscr{I},\iota\right)$ is additive
but non-convex, there are three numbers\nb$x_{0}$, $x_{1}$, and
$x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
Consider a 4-dimensional Hilbert space and a density matrix
\begin{equation}
\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\textrm{ .}
\end{equation}
Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$, and $\bar{\mu}\left(P\right)=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)\right)$.
Then,
\begin{equation}\eqalign{ 
 & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)
=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\ 
= & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)
\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\\ 
= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)
=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ .} 
}\end{equation}
\end{proof}

>>>>

\documentclass[12pt]{iopart}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage{cmap}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{0229}{\c{e}}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}

@@

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[3] }
\newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
\newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}

@@

This section extend the idea of restricting the event space, but instead
of commuting sub-event space, we will try to find some subset~$\events'\subseteq\events$
such that $\bar{\mu}|_{\events'}$ has an non-empty core. This could
help us understand the core because of the following identity
\begin{equation}
\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\label{eq:core-intersection}
\end{equation}
if we know more about the right-hand side of the equation, we can
have more idea about the left-hand side. This idea can be applied
to example~\ref{ex:three-dimensional-three-value}, and the following
are three of all possibilities:
\begin{itemize}
\item When $\events_{1}=\events\backslash\left\{ \proj{\ps'}\right\} $,
because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have
$\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} $.
\item When $\events_{2}=\events\backslash\left\{ \proj{\ps}\right\} $,
because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, we
have $\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} $.
\item When $\events_{3}=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$,
we have $\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$
as well as $\mu_{\ket{2}}^{\mathrm{B}}$ and $\mu_{\ket{1}}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$.
\end{itemize}
Each of these possibilities is compatible with some but not all of
the observations. In another word, 
\begin{equation}
\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{\mathrm{B}}\right\} \cap\left\{ \mu_{\ket{1}}^{\mathrm{B}}\right\} =\emptyset\textrm{ .}
\end{equation}
The first two possibilities are particular interesting since each
two 1-dimensional projectors\nb$\proj{\psi_{0}}$ and $\proj{\psi_{1}}$
mapped to $\imposs$ suggests there is a subset~$\events'\subseteq\events$
such that $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{\mathrm{B}}\right\} $
in the Hilbert space of dimension 3, where the cross product of complex
vectors is defined in definition~\ref{def:cross-product}.

@@

In order to simplify the discussion, we call a function\nb$\bar{f}:S^{2}\rightarrow\mathscr{I}$
satisfying conditions in theorem~\ref{thm:interval-valued-frame-function}
a real interval-valued frame function. Obviously, any results in appendix~\ref{sec:Interval-valued-Frame-Functions}
still hold if we replace every ``complex'' by ``real,'' in particular,
replace every $\mathbb{C}S^{2}$ by $S^{2}$. Furthermore, since restricting
the domain of a complex interval-valued frame function to $S^{2}$
gives a real interval-valued frame function, if we prove there is
no real interval-valued frame function satisfying a condition, then
there must be no complex interval-valued frame function satisfying
the corresponding condition. From now on, when we write an interval-valued
frame function~$\bar{f}$ without other specification, we would always
means a real interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$.

@@

\begin{proof}When $\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$,
$\bar{\mu}$ and $\bar{\mu}^{\Omega}$ are essentially quantum and
classical real-valued probability measures, respectively. Hence, it
is sufficient to prove the interval-valued case.
\begin{itemize}
\item $\bar{\mu}^{\Omega}(\emptyset)=\bar{\mu}\left(\sum_{\ket{j}\in\emptyset}\proj{j}\right)=\bar{\mu}\left(\mathbb{0}\right)=[0,0]$. 
\item $\bar{\mu}^{\Omega}(\Omega)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)=[1,1]$. 
\item For any event $E\in2^{\Omega}$,
\begin{equation}
\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .}
\end{equation}
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$
of pairwise disjoint events, we have
\begin{equation}
\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}^{\Omega}\left(E_{i}\right)\textrm{ .}
\end{equation}
\end{itemize}
\end{proof}

@@

For case \ref{enu:sub-event-space-real-classical2quantum}, if we
pick $\rho=\sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\proj{j}$,
then $\rho$ is a density matrix because~\cite{544199}
\begin{eqnarray}
\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\Tr\left(\proj{j}\right)=1\textrm{ .}
\end{eqnarray}
Also, 
\begin{eqnarray*}
 &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)
 =\sum_{j=1}^{N}\mu'\left(\left\{ j\right\} \right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)
 =\mu'\left(\left\{ j\right\} \right)
 =\mu'\left(\tau\left(\proj{i}\right)\right)\textrm{ for all }i\textrm{ ,}\\
 &  & \mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)
 \overset{\textrm{IH}}{=}\mu'\left(\tau\left(P_{1}\right)\right)+\mu'\left(\tau\left(P_{2}\right)\right)
 =\mu'\left(\tau\left(P_{1}+P_{2}\right)\right)
\end{eqnarray*}
for commuting\nb$P_{0},P_{1}\in\events$ with $P_{0}P_{1}=\mathbb{0}$.
Therefore, we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\widehat{\events}$ by induction.\end{proof}

@@

\begin{proof}Given two events~$E_{0},E_{1}\subseteq\Omega$, we
want to verify 
\begin{equation}
\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .}\label{eq:classical-convex}
\end{equation}
When $E_{0}\cap E_{1}=\emptyset$, equation~(\ref{eq:classical-convex})
is a special case of equation~(\ref{eq:classical-include}). When
$E_{0}\cup E_{1}=\Omega$, we have $E_{0}^{c}\cap E_{1}^{c}=\emptyset$,
where $E_{0}^{c}=\Omega\backslash E_{0}$ and $E_{1}^{c}=\Omega\backslash E_{1}$.
Thus, 
\begin{equation}\eqalign{ 
& \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\ 
\Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\ 
\Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\textrm{ .} 
}\end{equation}
When the number of elements in $\Omega\le3$, either $E_{0}\cap E_{1}=\emptyset$
or $E_{0}\cup E_{1}=\Omega$ must happen so that $\bar{\mu}^{\Omega}$
is convex. \end{proof}

@@

\begin{proof}Since $\left(\mathscr{I},\iota\right)$ is additive
but non-convex, there are three numbers\nb$x_{0}$, $x_{1}$, and
$x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
Consider a 4-dimensional Hilbert space and a density matrix
\begin{equation}
\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\textrm{ .}
\end{equation}
Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$, and $\bar{\mu}\left(P\right)=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)\right)$.
Then,
\begin{equation}\eqalign{ 
 & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\ 
= & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)
\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\\ 
= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)
=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ .} 
}\end{equation}
\end{proof}
